%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Bryan Oliveira} \\ \vspace{1pt}
    \small
    \href{https://github.com/BryOliveira}{\raisebox{-0.1\height}{\faGithub \scriptsize} \underline{\smash{github.com/BryOliveira}}} ~
    \href{mailto:bryoliveira2004@gmail.com}{\raisebox{-0.1\height}{\faEnvelope \scriptsize} \underline{\smash{bryoliveira2004@gmail.com}}} ~
    \href{https://linkedin.com/in/bryan-r-oliveira/}{\raisebox{-0.1\height}{\faLinkedin \scriptsize} \underline{\smash{linkedin.com/in/bryan-r-oliveira}}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Institute of Technology}{Expected: Jun. 2026}
      {Bachelor of Science in Computer Science $|$ GPA: 3.7}{Pasadena, CA}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-4pt, parsep=5pt]
                \item\small Object-Oriented Programming
                \item Algorithms and Complexity Analysis
                \item Data Structures
                \item Software Design
                \item Systems Programming
                \item Deep Learning Systems
                \item Relational Databases
                \item Differential Equations
                \item Probability Models
                \item Web Development
                \item Machine Learning and Data Mining
                \item Integrated Circuits
            \end{itemize}
        \end{multicols}
    %\resumeSubHeadingListEnd
\vspace{-5pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, C, C++, HTML, CSS, MySQL, Java, MATLAB} \\
     \textbf{Frameworks/Libraries}{: Node.js, Express, PyTorch, sklearn, pandas, Matplotlib, NumPy, CUDA, REST APIs, Fetch API} \\
     \textbf{DevOps \& Other}{: Git, VSCode, Linux, WSL, LaTeX}
    }}
 \end{itemize}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Navy Federal Credit Union}{Jun. 2024 -- Sep. 2024}
      {Software Engineer Intern}{Vienna, VA}
      \resumeItemListStart
        \resumeItem{Engineered internal SharePoint portals for the Security, Financial, and Fraud teams consisting of 60+ users with up-to-date information after organizational restructuring.}
        \resumeItem{Designed 30+ custom UI icons and infographics using HTML, CSS, and JavaScript, strengthening branding and enhancing UI/UX cohesion.}
        \resumeItem{Spearheaded development of a JavaScript org-chart creation web app to replace static diagrams and to enable real-time structural updates for all $\sim$24,000 employees.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Comeback: Full-stack E-commerce Site with RESTful API} $|$ \emph{JavaScript, Node.js, Express}}{May -- Jun. 2025}
    \resumeItemListStart
      \resumeItem{Used the Fetch API to build a RESTful API backend supporting dynamic routes for products, FAQs, user feedback, and loyalty program endpoints.}
      \resumeItem{Managed front-end with HTML/CSS and JavaScript and handled backend logic with Node.js and Express to create route definitions, request validation, and error handling.}
      \resumeItem{Implemented user authentication for loyalty program signup/login and a feedback form using POST requests.}
    \resumeItemListEnd
  \vspace{-16pt}
  \resumeProjectHeading
    {\textbf{Affor-db: House Affordability Database Application} $|$ \emph{Python, MySQL}}{Feb. -- Mar. 2025}
    \resumeItemListStart
      \resumeItem{Co-created a CLI tool integrating a MySQL database with housing, mortgage, and job market datasets to generate personalized affordability metrics across 450+ jobs and 350+ companies across all U.S. states.}
    \resumeItemListEnd
  \vspace{-16pt}
  \resumeProjectHeading
    {\textbf{Leggies: Physics-Based Fighting Game} $|$ \emph{C, GitLab}}{May -- Jun. 2024}
    \resumeItemListStart
      \resumeItem{Constructed a 1v1 multiplayer fighting game with collision detection, sprite animation, and combat logic.}
      \resumeItem{Developed a custom physics engine in C for applying object-oriented design patterns for entity behavior.}
      \resumeItem{Collaborated with a 3-person team using GitLab, resolving merge conflicts and optimizing shared code structure.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurriculars}
    \textbf{Caltech Hispanic and Latino Association (SHPE Chapter)}
    \begin{tabularx}{\textwidth}{Xr}
        \textit{\small Outreach Coordinator} & \textbf{\small Jun. 2025 -- Present} \\
        \textit{\small Social Director} & \textbf{\small Jun. 2024 -- Jun. 2025}
    \end{tabularx}
    \vspace{2pt}
    \textbf{Caltech Sunday League Soccer}
    \begin{tabularx}{\textwidth}{Xr}
        \textit{\small Captain} & \textbf{\small Feb. 2023 -- Present}
    \end{tabularx}
    \vspace{2pt}
    \textbf{Caltech First-Year Success Research Institute}
    \begin{tabularx}{\textwidth}{Xr}
        \textit{\small Peer Mentor} & \textbf{\small Jul. 2023 -- Sep. 2023}
    \end{tabularx}

\end{document}
